---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nord: Northern-themed Color palettes

[![Build Status](https://travis-ci.org/jkaupp/nord.svg?branch=master)](https://travis-ci.org/jkaupp/nord)

The goal of nord is to provide access to many northern inspired palettes:

 1. 4  colour palettes from [ArticIceStudio's Nord Palettes](https://git.io/nord) 
 2. 1 color palette extracted from [Lumina Borealis](https://www.luminaborealis.com/)
 3. 11 colour palettes extracted from the works of the [Group of Seven](https://en.wikipedia.org/wiki/Group_of_Seven_(artists))
 
These palettes can be used both with `ggplot2`, `lattice` and base R plotting to provide color to charts and graphics.  The palettes in `nord` try to split equally between qualitiative, sequential and diverging data, similar to the categories used in [ColorBrewer](http://colorbrewer2.org/).  Further information and use of each palette can be found in the vignette.

## Installation

You can install nord from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jkaupp/nord")
```

## The Palettes of `nord`

```{r palettes}
library(nord)

par(mfrow=c(8, 2), lheight = 2, mar=rep(1, 4), adj = 0)

lapply(names(nord_palettes), nord_show_palette)

```


## Example

This is a basic example which shows you how to use the different features in `nord`:

Here is how to use `scale_fill_nord()` with `ggplot2` 
```{r ggplot2_example}
library(ggplot2)
library(nord)

ggplot(diamonds) + 
  geom_bar(aes(x = cut, fill = clarity)) +
  scale_fill_nord("victory_bonds")
```

Here is using the `nord` function, with built in color-ramping, with the obligatory base r volcano.

```{r plot_example}
image(volcano, col = nord("aurora", 20))
```

You can view the individual palettes in `nord` via `nord_show_palette()`

```{r show_palette}
nord_show_palette("baie_mouton")
```


